%-------------------------
% Tailored Resume for Base ML Engineer
% Author : Ameya Vinay Panchpor
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1
\setstretch{0.2}

\newcommand{\resumeItem}[1]{
  \item[$\vcenter{\hbox{\tiny$\bullet$}}$]\small{
    #1 \vspace{-2pt}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\small #1}, \textit{\small #3} & {\small #2} \\
    & \textit{\small \textcolor{black}{#4}} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%-------------------- HEADING --------------------
\begin{center}
    \textbf{\Huge \scshape Ameya Vinay Panchpor} \\ \vspace{5pt}
    San Jose, CA $|$ (408) 396-2910 $|$
    \href{mailto:ameya.panchpor@gmail.com}{ameya.panchpor@gmail.com} $|$
    \href{https://www.linkedin.com/in/ameya-panchpor}{linkedin.com/in/ameya-panchpor} $|$
    \href{https://github.com/ameya690}{github.com/ameya690}
\end{center}

%-------------------- EDUCATION --------------------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University, San Jose, CA}{Aug 2023 – Dec 2025}
      {Master of Science in Artificial Intelligence}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Machine Learning, Natural Language Processing, Data Mining, Computer Vision, Advanced Data Structures, Operating Systems}
      \resumeItemListEnd

    \resumeSubheading
      {University of Pune, Pune, India}{Aug 2018 – Jul 2022}
      {Bachelor of Technology in Computer Engineering}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Data Structures, Python/C Programming, Computer Vision, Control Systems, Industrial Automation}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------- SKILLS --------------------
\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
  \textbf{Programming:} Python, Java, C++, SQL, Bash \\
  \textbf{ML/AI:} Probabilistic/Statistical Modeling, Transformers, Deep Neural Networks, Scikit-learn, TensorFlow, PyTorch, XGBoost \\
  \textbf{Data \& NLP:} Large-Scale Dataset Curation, Text Preprocessing, Semantic Retrieval, Spark, Pandas, NumPy \\
  \textbf{Infrastructure:} Docker, Kubernetes, AWS, GCP, CI/CD, TorchScript, ONNX \\
  \textbf{Databases:} PostgreSQL, MongoDB, Redis
}}
\end{itemize}

%-------------------- EXPERIENCE --------------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Machine Learning Engineer} $|$ \emph{Aftershoot Inc.}}{Jan 2023 – Jun 2023}
\resumeItemListStart
  \resumeItem{Built and deployed an end-to-end \textbf{computer vision pipeline} (\textbf{face detection}, \textbf{blur filtering}, \textbf{keypoint estimation}) to auto-rank image quality using \textbf{AWS SageMaker}, accelerating throughput by \textbf{25\%}.}
  \resumeItem{Deployed optimized deep learning models with \textbf{TorchScript} and \textbf{ONNX Runtime} on \textbf{AWS EC2} and \textbf{GCP Compute Engine}, enabling low-latency photo culling and reducing manual effort by \textbf{30\%}.}
  \resumeItem{Enhanced pose estimation accuracy by \textbf{5\%} through model quantization and architecture refinement.}
  \resumeItem{Collaborated with infrastructure teams to streamline model deployment on edge devices, integrating with \textbf{AWS S3} for scalable storage and ensuring real-time performance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Data Scientist} $|$ \emph{FITT, Indian Institute of Technology Delhi}}{Aug 2022 – Jan 2023}
\resumeItemListStart
  \resumeItem{Engineered a data pipeline using \textbf{PostgreSQL} and \textbf{Python} that reduced aggregation time by \textbf{50\%}.}
  \resumeItem{Developed \textbf{XGBoost} models for sepsis (\textbf{98.4\%} accuracy) and AMR detection (\textbf{98.1\%} accuracy), leveraging \textbf{time-series} data analysis with \textbf{Spark}.}
  \resumeItem{Enabled anomaly detection via \textbf{Python-SQL} workflows, improving data interpretability.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI Engineer} $|$ \emph{Indian Institute of Technology BHU, Varanasi}}{Mar 2020 – Dec 2020}
\resumeItemListStart
  \resumeItem{Built \textbf{CNN}-based CT scan classifiers that improved diagnostic accuracy by \textbf{25\%}.}
  \resumeItem{Automated NLP-driven literature mining with \textbf{NLTK}, expediting outlier detection by \textbf{40\%}.}
  \resumeItem{Deployed real-time prediction workflows using \textbf{GCP}, boosting forecast precision by \textbf{15\%}.}
  \resumeItem{Integrated \textbf{OpenCV}, \textbf{Kafka}, and \textbf{Airflow} for surveillance, enhancing crowd recognition by \textbf{35\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- PROJECTS --------------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Koe: Universal Voice \& Chat Customer Support System} $|$ \emph{Llama3, Claude, AWS Bedrock, MongoDB}}{}
\resumeItemListStart
  \resumeItem{Developed an LLM-driven customer support agent, awarded Best Project at MongoDB GenAI Hackathon, for automating multi-modal query resolution across websites.}
  \resumeItem{Engineered a web scraping and FAQ graph generation pipeline, stored in a MongoDB vector store, improving query accuracy by \textbf{30\%} using semantic retrieval.}
  \resumeItem{Integrated \textbf{LLaMA 3} with Vocode API for real-time voice support, enabling phone-call-based interaction and reducing user response latency by \textbf{40\%}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{weeRAG: Minimal LLM \& RAG Framework} $|$ \emph{PyTorch, Transformers, NumPy}}{}
\resumeItemListStart
\resumeItem{Developed a GPT-style transformer with \textbf{KV caching} and post-training \textbf{int8/4 quantization}, reducing model size by \textbf{$>$90\%} while retaining \textbf{95\% perplexity}.}
\resumeItem{Created an evaluation suite with \textbf{EM/F1, faithfulness, hybrid reranker, and LLM-as-judge}, enabling automated benchmarking of retrieval pipelines.}
\resumeItem{Built modules for \textbf{synthetic QA generation, knowledge graph extraction, and guardrails}, improving RAG interpretability, safety, and auditability.}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{RoadRep-LoRA: Road Scene Understanding System} $|$ \emph{PyTorch Lightning, ONNX, Docker, Streamlit}}{}
  \resumeItemListStart
    \resumeItem{Built an end-to-end system for road scene understanding: dataset preprocessing (\textbf{30k+} frames), \textbf{BLIP}-based auto-captioning, \textbf{LoRA} fine-tuning, and \textbf{ONNX} deployment.}
    \resumeItem{Quantized for CPU inference at \textbf{6 FPS}, and \textbf{Dockerized} the workflow for reproducible deployment.}
    \resumeItem{Developed evaluation pipelines (retrieval, zero-shot classification) and a \textbf{CLI}/\textbf{Streamlit} demo for real-time scene querying.}
  \resumeItemListEnd

\resumeProjectHeading
{\textbf{3D Scene Understanding via Stereo Imaging} $|$ \emph{Python, OpenCV, NumPy, CloudCompare}}{}
\resumeItemListStart
  \resumeItem{Developed disparity-based 3D reconstruction system using stereo imaging and spatial filters.}
  \resumeItem{Visualized point clouds in CloudCompare to simulate spatial mapping for autonomous agents.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Artificially Abled: Gesture-to-Text Translation System} $|$ \emph{Python, TensorFlow, OpenPose, RNN, LSTM}}{}
\resumeItemListStart
  \resumeItem{Developed a real-time gesture recognition system achieving \textbf{92\%} classification accuracy using \textbf{LSTM}-based temporal modeling.}
  \resumeItem{Utilized \textbf{OpenPose} for landmark extraction across \textbf{10,000+} labeled sequences, enabling robust motion analysis.}
  \resumeItem{Achieved $<$\textbf{150ms} latency on edge devices using dropout-regularized lightweight models.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Perplexity for Images: Zero-Shot Object Search System} $|$ \emph{Python, Scikit-learn, OpenCV}}{}
\resumeItemListStart
  \resumeItem{Built a scalable NLP-driven computer vision pipeline with Grounded SAM, achieving \textbf{98\%} accuracy in zero-shot object detection for personalized queries.}
  \resumeItem{Implemented a distributed reverse image search system with Redis, improving retrieval precision by \textbf{15\%} and latency by \textbf{40\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- PUBLICATIONS & AWARDS --------------------
\section{\textbf{Publications \& Awards}}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{MongoDB GenAI Hackathon 2024} $|$ \emph{Mountain View, CA}}{}
    \resumeItemListStart
      \resumeItem{Awarded \textbf{Best Project} for developing Koe — LLM-driven customer support system with semantic retrieval and real-time voice integration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{ThyCaps: Capsule Network Based Thyroid Lesion Detection} $|$ \emph{Seybold Report, 2022}}{}
    \resumeItemListStart
      \resumeItem{First authored peer-reviewed research on applying Capsule Networks for medical imaging diagnostics.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------- ACHIEVEMENTS --------------------
\section{\textbf{Achievements}}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Hackathons (5× Winner)}}{}
    \resumeItemListStart
      \resumeItem{Recognized for innovative ML/AI solutions across Bay Area competitions.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Google Developer Student Club, Pune}}{}
    \resumeItemListStart
      \resumeItem{Mentored \textbf{400+ students} in ML and programming, fostering community learning.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{CovidScope — Pandemic Resource Portal}}{}
    \resumeItemListStart
      \resumeItem{Built and launched a public portal for pandemic resources, featured by local media outlets.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
