%-------------------------
% Tailored Resume for Software Development Engineer
% Author : Ameya Vinay Panchpor
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1
\setstretch{0.2}

\newcommand{\resumeItem}[1]{
  \item[$\vcenter{\hbox{\tiny$\bullet$}}$]\small{
    #1 \vspace{-2pt}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\small #1}, \textit{\small #3} & {\small #2} \\
    & \textit{\small \textcolor{black}{#4}} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%-------------------- HEADING --------------------
\begin{center}
    \textbf{\Huge \scshape Ameya Vinay Panchpor} \\ \vspace{5pt}
    San Jose, CA $|$ (408) 396-2910 $|$
    \href{mailto:ameya.panchpor@gmail.com}{ameya.panchpor@gmail.com} $|$
    \href{https://www.linkedin.com/in/ameya-panchpor}{linkedin.com/in/ameya-panchpor} $|$
    \href{https://github.com/ameya690}{github.com/ameya690}
\end{center}

%-------------------- EDUCATION --------------------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University, San Jose, CA}{Aug 2023 – Dec 2025}
      {Master of Science in Artificial Intelligence}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Machine Learning, Natural Language Processing, Data Mining, Computer Vision, Advanced Data Structures, Operating Systems}
      \resumeItemListEnd

    \resumeSubheading
      {University of Pune, Pune, India}{Aug 2018 – Jul 2022}
      {Bachelor of Technology in Computer Engineering}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Data Structures, Python/C Programming, Computer Vision, Control Systems, Industrial Automation}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------- SKILLS --------------------
\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
  \textbf{Programming:} Python, Java, C++, SQL, Bash \\
  \textbf{ML/AI:} Probabilistic/Statistical Modeling, Transformers, Deep Neural Networks, Scikit-learn, TensorFlow, PyTorch, XGBoost \\
  \textbf{Data \& NLP:} Large-Scale Dataset Curation, Text Preprocessing, Semantic Retrieval, Spark, Pandas, NumPy \\
  \textbf{Infrastructure:} Docker, Kubernetes, AWS, GCP, CI/CD, TorchScript, ONNX \\
  \textbf{Databases:} PostgreSQL, MongoDB, Redis
}}
\end{itemize}

%-------------------- EXPERIENCE --------------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Software Engineer} $|$ \emph{Aftershoot Inc.}}{Jan 2023 – Jun 2023}
\resumeItemListStart
  \resumeItem{Developed RESTful APIs with \textbf{Flask} to integrate ML models into production, improving modularity and enabling seamless updates.}
  \resumeItem{Optimized computer vision pipelines (\textbf{pose detection, body segmentation}) using \textbf{PyTorch} and \textbf{Keras}, improving accuracy by \textbf{20\%}.}
  \resumeItem{Collaborated using Agile and SDLC practices; reduced image processing time by \textbf{25\%} and manual culling time by \textbf{30\%}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Software Engineer} $|$ \emph{FITT, Indian Institute of Technology Delhi}}{Aug 2022 – Jan 2023}
\resumeItemListStart
  \resumeItem{Developed an automated invoice management system using \textbf{Python, Flask, PostgreSQL}, reducing manual processing time by \textbf{50\%}.}
  \resumeItem{Built a web dashboard with \textbf{Flask, MySQL} for real-time invoice tracking, streamlining financial operations.}
  \resumeItem{Implemented a \textbf{React} frontend to visualize real-time payment data, enhancing financial decision-making.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Software Intern} $|$ \emph{Indian Institute of Technology BHU, Varanasi}}{Mar 2020 – Dec 2020}
\resumeItemListStart
  \resumeItem{Developed scalable data pipelines in \textbf{Python, Pandas} to process transcriptomics datasets, improving reproducibility of molecular inference.}
  \resumeItem{Built \textbf{deep learning classifiers} (PyTorch) for medical imaging, improving CT scan diagnostic accuracy by \textbf{25\%}.}
  \resumeItem{Mined \textbf{44k+ research articles} using \textbf{Databricks, NLTK}, enabling anomaly detection and expediting biomedical analysis by \textbf{40\%}.}
  \resumeItem{Engineered forecasting models with \textbf{Scikit-learn, Pandas} on \textbf{GCP}, improving COVID-19 trend prediction accuracy by \textbf{15\%}.}
  \resumeItem{Implemented \textbf{Kafka} and \textbf{Airflow} for real-time surveillance data streaming, enhancing detection efficiency by \textbf{35\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -------------------- PROJECTS --------------------
\vspace{-3pt}
\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{weeRAG: Minimal LLM \& RAG Framework} $|$ \emph{PyTorch, FastAPI, SQLite, NumPy}}{}
\resumeItemListStart
\resumeItem{Built an end-to-end open-source RAG framework with \textbf{20+ modular components} covering tokenization, retrieval, routing, caching, and streaming.}
\resumeItem{Implemented a \textbf{vector store, retriever, and router} achieving sub-\textbf{100ms retrieval latency}, and integrated \textbf{FastAPI SSE streaming} for low-latency token delivery.}
\resumeItem{Developed a \textbf{SQLite-backed caching layer} and tracing utilities for reproducible, scalable inference pipelines.}
\resumeItemListEnd


\resumeProjectHeading
         {\textbf{ConnectSphere:A scalable microblogging platform} $|$ \footnotesize\emph{React, Next.js, Chakra UI, GraphQL, PostgreSQL, Node.js, Express.js, Redis}}

        \resumeItemListStart
            \resumeItem{Designed and developed a scalable microblogging platform leveraging React, TypeScript, Node.js, GraphQL, and PostgreSQL, demonstrating comprehensive full-stack development capabilities and integration of diverse technologies.}
            \resumeItem{Implemented advanced security measures including two-factor authentication and OAuth for Google sign-in, strengthening platform security.}
            \resumeItem{To ensure the application’s reliability and code quality, we automated regression testing through a robust CI/CD pipeline using Jenkins and GitLab CI}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Cloud Native Message Queue System} $|$ \emph{Python, Raft, Kafka, Docker}}{}
\resumeItemListStart
  \resumeItem{Designed a \textbf{Kafka}-inspired multi-cluster architecture, with \textbf{3-5} brokers per cluster for scalable message streaming.}
  \resumeItem{Implemented \textbf{Raft} protocol, achieving \textbf{99.9\%} data consistency and synchronization across distributed brokers.}
  \resumeItem{Deployed system using \textbf{Docker}, reducing setup time by \textbf{40\%} and enabling fault-tolerant streaming.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Distributed File Storage System} $|$ \emph{Golang, MongoDB, Kubernetes}}{}
\resumeItemListStart
  \resumeItem{Built a distributed file storage system using \textbf{Golang}, achieving \textbf{50\%} reduction in read/write latency.}
  \resumeItem{Integrated \textbf{MongoDB} for metadata storage and \textbf{Kubernetes} for orchestration, ensuring \textbf{99.9\%} uptime.}
  \resumeItem{Optimized data retrieval with caching, improving throughput by \textbf{40\%} for high-volume access.}
\resumeItemListEnd
        
\resumeProjectHeading
{\textbf{HPC for Parallel Data Analysis of the NYC Parking Dataset} $|$ \footnotesize\emph{MPI, OpenMP, C++, Python, Flask, Distributed technology}}
         
\resumeItemListStart
\resumeItem{Significantly executed data extraction and processing on a 21 GB NYC parking violation dataset with over 10 million rows and 43 columns, achieving a 60\% reduction in total execution time by implementing parallel processing techniques with \textbf{OpenMPI} and \textbf{MPI}.}
\resumeItem{Enhanced system reliability and monitoring in distributed environments with advanced logging and debugging, alongside meticulous performance benchmarking of parallel processes, identifying optimal performance at 4 concurrent processes}
\resumeItemListEnd

%-------------------- PUBLICATIONS & AWARDS --------------------
\section{\textbf{Publications \& Awards}}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{MongoDB GenAI Hackathon 2024} $|$ \emph{Mountain View, CA}}{}
    \resumeItemListStart
      \resumeItem{Awarded \textbf{Best Project} for Koe — LLM-driven customer support system with semantic retrieval and real-time voice integration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{ThyCaps: Capsule Network Based Thyroid Lesion Detection} $|$ \emph{Seybold Report, 2022}}{}
    \resumeItemListStart
      \resumeItem{Co-authored peer-reviewed research on Capsule Networks for medical imaging diagnostics.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------- ACHIEVEMENTS --------------------
\section{\textbf{Achievements}}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Hackathons (5× Winner)}}{}
    \resumeItemListStart
      \resumeItem{Recognized for innovative ML/AI solutions across Bay Area competitions.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Google Developer Student Club, Pune}}{}
    \resumeItemListStart
      \resumeItem{Mentored \textbf{400+ students} in ML and programming, fostering community learning.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{CovidScope — Pandemic Resource Portal}}{}
    \resumeItemListStart
      \resumeItem{Built and launched a public portal for pandemic resources, featured in local media.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
